Flow-Directed Trace Analysis for Post-Silicon Validation

### 2015-08-17 paper.tex
minor

By combining information from all 9 of the communicate monitors, we will have all the communication traces we need. As an virtualized SOC platform, GEM5 has two types of request, timing and atomic. Timing is what will be used in our system as it simulate delays generated by 
During our experiment, we took only timing request from the raw traces to eliminate initiation traces that are useless for our research.

@@

In this case study, two system flows are implemented in the SoC model. They include a cache coherent read request from CPU and a cache coherent write request from CPU. In the following , a brief overview for the implemented instances of these flows is given. These flow specifications capture how messages are exchanged for different use cases. In this model, a message is defined with the following format, (Src,Dest,Cmd), where Src and Dest refer to the source and destination components of messages, Cmd refers to the operations that the destination component should perform. 
\begin{figure} 
\centerline{
\includegraphics[width=3.7In]{figures/Fig5.png}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Results and Discussions}

The transaction level model of the simple system implementing the two flow specifications shown in the previous section is implemented by Gem5. We build a simple platform in Gem5 with components described in Fig~\ref{SOC}. By running two simple executables on each CPU simultaneously, we produce a result file including all the communication between each components. The executable assigned to CPU1 is read one file three times for one letter and writing one letter for three times to the same file. CPU2's executable will do the same functionality to the same file, only difference is that CPU2 will write first and then read.

>>>>

By combining information from all 9 of the communicate monitors, we will have all the communication traces we need. As an virtualized SOC platform, GEM5 has three types of request: timing, atomic and functional. Timing request are the most detailed request. This type of request include the modeling of queuing delay and resource contention. A successfully sent timing will receive an response at some point in the future. Atomic accesses are a faster than detailed access. They are used for fast forwarding and warming up caches and return an approximate time to complete the request without any resource contention or queuing delay. Functional accesses are used for things such as loading binaries, examining/changing variables in the simulated system, and allowing a remote debugger to be attached to the simulator. In our case, we specified all our request to be timing. However, some of the system initiation is still atomic and it's useless for our research, so we only took the messages that are timing request from our collected data. (From GEM5 online documentaries)

@@

In this case study, two system flows are implemented in the SoC model. They include a cache coherent read request from CPU and a cache coherent write request from CPU. To avoid messages that are not included in this two flow, like write back, cache flushing, we only use data that is related to these two flow.

In the following , a brief overview for the implemented instances of these flows is given. These flow specifications capture how messages are exchanged for different use cases. In this model, a message is defined with the following format, (Src,Dest,Cmd), where Src and Dest refer to the source and destination components of messages, Cmd refers to the operations that the destination component should perform. 
\begin{figure} 
\centerline{
\includegraphics[width=3.7In]{figures/Fig5.png}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Results and Discussions}
We produce a result file including all the communication between each components by running two simple programs on each CPU simultaneously, . The executable assigned to CPU1 is read one file three times for one letter and writing one letter for three times to the same file. CPU2's executable will do the same functionality to the same file, only difference is that CPU2 will write first and then read. One thing we should know about GEM5 is that even if we specify these two program two be ran concurrently, and GEM5 try to produce an concurrent result. The data we collected shows that it's not the real nondeterministic concurrency. What GEM5 did is letting the two CPU execute one instruction in turn, so the order is determined, no matter how many time we run the program, it will always produce the same result. We tried other virtual SOC platform softwares, and this is the best nondeterministic concurrency we can get. Even if this is slightly off with what the real chip should work, it still suit our purpose of testing the correctness of our algorithm.

As we mentioned before, we will take away unrelated messages for easier testing purpose. After taking out non-timing request, the number of communication messages reduced from 343581 to 133676, and after removing the message that's not related to tested flow specification, number of messages became 120949.
